Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.5.0, fix typos.

\def\cvprPaperID{6666} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
On the computer hardware, compared the $8508*8508$ matrix multiplication time-cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.

@@

For a fully connected network, the graph has a maximum diameter of $n-1$, so using the result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times are $log_2(n-1)$.
Albert~\cite{albert1999diameter} found that social networks, the Internet, and other complex networks have scale-free characteristics and small-world phenomena, thus network diameter is much smaller than the number of network nodes.
I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
thus Alon \etal algorithm time-bound is \(O(\log{\Bbb D}2n^3\over \Bbb B)\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O(\log(\log{N})2n^3\over \Bbb B)\).
With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D} \approx \log(\log{N})<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
bringing a stronger time-bound of \(O(14n^3\over \Bbb B)\).
In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O(14n^3\over \Bbb B)\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).

@@

Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
\begin{equation}
\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
\begin{equation}
a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
\end{equation}

Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
\begin{equation}
  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
\begin{equation}
a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
\end{equation}
%-------------------------------------------------------------------------
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
\end{center}
   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network. (a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
\label{fig:short}
\end{figure*}

@@

\begin{algorithm}
\caption{Lower Bounds Convergence Matrix Products in All-Pairs Shortest Path}\label{algorithm}
\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
\KwResult{The shortest path result $L^{(m)}$}
  $L^{(1)}\leftarrow \Bbb W$\;
  $m\leftarrow 1$\;
  \While{$m\leq \Bbb D$}{
    $\Bbb A\leftarrow L^{(m)},\Bbb B\leftarrow L^{(m)},$\;
    $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
    The exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
      $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
      $b_{ij}^{'}={(n+1)}^{y-b_{ij}}$\;
    \eIf{$L^{(m)}$ is sparse}{
      $\odot\leftarrow \bigcirc$//sparse matrix multiplication\;
    }{
      $\odot\leftarrow \otimes$//dense matrix multiplication\;
    }
    Given matrices $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
    $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
    The logrithm transformation of matrix $\Bbb C^{'}$\;
    $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
    \If{$L^{(m)} = \Bbb C$}{
      {\bf return} $L^{(m)}$\;
    }
    $L^{(2m)}\leftarrow \Bbb C$\;
    $m\leftarrow 2*m$\;
  }
  {\bf return} $L^{(m)}$\;
\end{algorithm}

>>>>

\def\cvprPaperID{6666} % \times \times \times  Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
On the computer hardware, compared the $8508\times 8508$ matrix multiplication time-cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.

@@

For a fully connected network, the graph has a maximum diameter of $n-1$, so using the result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times are $log_2(n-1)$.
Albert~\cite{albert1999diameter} found that social networks, the Internet, and other complex networks have scale-free characteristics and small-world phenomena, thus network diameter is much smaller than the number of network nodes.
I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
In social networks, the number of nodes $n$, with cache block size $B\times B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
thus Alon \etal algorithm time-bound is \(O({\log{\Bbb D}2n^3\over{ \Bbb B}})\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O({\log(\log{N})2n^3\over \Bbb B})\).
With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D} \approx \log(\log{N})<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
bringing a stronger time-bound of \(O({14n^3\over {\Bbb B}})\).
In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O({14n^3\over \Bbb B})\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).

@@

Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the outer product is:
\begin{equation}
\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m\times n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
\begin{equation}
a_{ij} = a_{ij} + x_i \times  y_j, i \in (1,m), j \in (1,n)
\end{equation}

Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the distance product is:
\begin{equation}
  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m\times n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
\begin{equation}
a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
\end{equation}
%-------------------------------------------------------------------------
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
\end{center}
   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network. (a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
\label{fig:short}
\end{figure*}

@@

\begin{algorithm}
\caption{Lower Bounds Convergence Matrix Products in All-Pairs Shortest Path}\label{algorithm}
\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
\KwResult{The shortest path result $L^{(m)}$}
  $L^{(1)}\leftarrow \Bbb W$\;
  $m\leftarrow 1$\;
  \While{$m\leq \Bbb D$}{
    $\Bbb A\leftarrow L^{(m)},\Bbb B\leftarrow L^{(m)},$\;
    $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
    The exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
      $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
      $b_{ij}^{'}={(n+1)}^{y-b_{ij}}$\;
    \eIf{$L^{(m)}$ is sparse}{
      $\odot\leftarrow \bigcirc$//sparse matrix multiplication\;
    }{
      $\odot\leftarrow \otimes$//dense matrix multiplication\;
    }
    Given matrices $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
    $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
    The logrithm transformation of matrix $\Bbb C^{'}$\;
    $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
    \If{$L^{(m)} = \Bbb C$}{
      {\bf return} $L^{(m)}$\;
    }
    $L^{(2m)}\leftarrow \Bbb C$\;
    $m\leftarrow 2\times m$\;
  }
  {\bf return} $L^{(m)}$\;
\end{algorithm}

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, fix typos.

  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved an accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 1	&	84.89\% \\
RBTL3  & CIFAR-10 & 1	&	97.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
RoBERTa-large & CIFAR-100 & 16 &	98.95\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an example for its performance in Computer Vision tasks.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set,
and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.

>>>>

  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved an accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 1	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
RoBERTa-large & CIFAR-100 & 16 &	98.95\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an example for its performance in Computer Vision tasks.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.5.0, fix typos.

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016earning}'s model.

@@

  Read \etal ~\cite{read2016earning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on Flowers dataset.

@@

\par \noindent Definition 1 (\textbf{Network Embedding})  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.

\par \noindent Definition 2 (\textbf{Shortest Path Network Embedding})  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.

>>>>

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016learning}'s model.

@@

  Read \etal ~\cite{read2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on Flowers dataset.

@@

\par \noindent Definition 1 (\textbf{Network Embedding})  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n\times n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n\times m)}$, $m < n$, where $m$ is an embedding dimension.

\par \noindent Definition 2 (\textbf{Shortest Path Network Embedding})  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n\times n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n\times n)}$, where $n$ is an embedding dimension.
